### 2017-01-17 robust-checks.tex
Submission to arXiv

\begin{easylist}[checklist]
& Have a README
&& Explain what the software does
&& List required dependencies
&& Provide compile/installation instructions
&& List input and output files
&& State attributions and licensing
& Print usage information from the command line
&& Include:
&&& the syntax for running the program in GNU/POSIX format
&&& a one line description
&&& the most commonly used arguments, a description of each, and the default values
&&&& Where to find more information
&& Print to standard output
&& Exit with an appropriate exit code
& Version your releases
&& Increment your version number every time you release your software to other people
&& Print when supplying \texttt{-\/-version} or \texttt{-v} on the command line
&& Include version number in output
&& Deposit releases in a stable location so they are available in perpetuity
& Reuse software (within reason)
&& Make sure that you really need the auxiliary program
&& Check for dependent software and version early in execution
&& Use native functions for starting other processes
& Use a build utilty and package manager
&& Document \emph{all} dependencies, preferably in a machine-readable form
&& Avoid depending on scripts and tools which are not available as packages
& Do not require root or other special privileges
&& Allow packages to be installed in an arbitrary location
&& Ask another person to try and build your software
& Eliminate hard-coded paths
&& Set the names and locations of input and output files as command-line parameters
&& Do not require users to navigate to a particular directory to do their work
& Allow configuration of all useful parameters from the command line.
&& Choose reasonable defaults where they exist
&& Set no defaults at all when there aren't any reasonable ones
&& Echo all parameters and software versions to standard out or a log file alongside the results
&& Check that all input values are in a reasonable range near startup
& Include a small test set that can be run to ensure the software is actually working.
&& Tests are easy to find and run
&& Test results are easy to interpret
& Produce identical results when given identical inputs
&& For randomized algorithms: allow the user to optionally provide the seed as an input parameter; or
&& Make sure the acceptable tolerance is known and detailed in documentation and in the tests
\end{easylist}

\section*{Bonus points}

\begin{easylist}[checklist]
& Conform to command-line conventions~\cite{Seemann2013}
& Write high quality documentation~\cite{karimzadeh2016}

@@

\bibliography{robust-checks}

>>>>

\begin{easylist}[checklist]
& Use version control.

& Document your code and usage
&& Explain what the software does.
&& List required dependencies.
&& Provide compilation/installation instructions.
&& List input and output files.
&& State attributions and licensing.
&& Print usage information when launching from the command line.
&& Desribe the syntax for running the program.
&& Explain the software's primary function.
&& Describe the most commonly used arguments, with a description of each and default values.
&& Tell users where to find more information.
&& Print to standard output.
&& Exit with an appropriate exit code

& Make common operations easy to control.
&& Allow the most commonly changed parameters to be configured from the command line.
&& Check that all input values are in a reasonable range at startup.
&& Choose reasonable defaults where they exist.
&& Set no defaults at all when there aren't any reasonable ones.

& Version your releases.
&& Increment your version number every time you release your software to other people.
&& Print the version number when given the appropriate flag.
&& Include the version number in all of the program's output.
&& Ensure that old released versions continue to be available.

& Reuse software (within reason).
&& Make sure that you really need auxiliary programs.
&& Ensure the appropriate software and version is available.
&& Ensure that reused software is robust.

& Rely on build tools and package managers for installation.
&& Document all dependencies in a machine-readable form.
&& Avoid depending on scripts and tools which are not available as packages.

& Do not require root or other special privileges to install or run.
&& Packages should not require root privileges to set up or use.
&& Allow packages to be installed in an arbitrary location.
&& Ask another person to try and build your software before releasing it.

& Eliminate hard-coded paths.
&& Set the names and locations of input and output files as command-line parameters.
&& Do not require users to navigate to a particular directory to do their work.

& Include a small test set that can be run to ensure the software is actually working.
&& Make the test script easy to find and run.
&& Make the test script's output easy to interpret.

& Produce identical results when given identical inputs.
&& Echo all parameters and software versions to standard out or a log file alongside the results.
&& A particular version of a program should produce the same results every time it is run.
&& Allow the user to optionally provide the random seed as an input parameter.
&& Make sure the acceptable tolerance is known and detailed in documentation and in the tests.

@@
